Predicting computational reproducibility of data analysis pipelines \\in large population studies using collaborative filtering

### 2018-11-11 paper.tex
Final version uploaded for IEEE BigData

% new commands
\newcommand{\todo}[1]{\marginpar{\parbox{18mm}{\flushleft\tiny\color{red}\textbf{TODO}:
      #1}}}
\newcommand{\note}[1]{
  \color{blue}\emph{[Note: #1]}
  \color{black}
}

@@

\begin{figure}
\centering
        %\begin{subfigure}[b]{\columnwidth}
                  %\includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/1_SubjectType_utility_matrix.png}
                  %\caption{1 type}
        %\end{subfigure}
        \begin{subfigure}[b]{0.45\columnwidth}
                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/2_SubjectType_utility_matrix.png}
                  \caption{2 types}
        \end{subfigure}
        \begin{subfigure}[b]{0.45\columnwidth}
                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/4_SubjectType_utility_matrix.png}
                  \caption{4 types}
        \end{subfigure}
                \begin{subfigure}[b]{0.45\columnwidth}
                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/8_SubjectType_utility_matrix.png}
                  \caption{8 types}
        \end{subfigure}
                \begin{subfigure}[b]{0.45\columnwidth}
                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/16_SubjectType_utility_matrix.png}
                  \caption{16 types}
        \end{subfigure}
                \begin{subfigure}[b]{0.45\columnwidth}
                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/32_SubjectType_utility_matrix.png}
                  \caption{32 types}
        \end{subfigure}
                \begin{subfigure}[b]{0.45\columnwidth}
                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/64_SubjectType_utility_matrix.png}
                  \caption{64 types}
        \end{subfigure}
\caption{Synthetic reproducibility matrices. White cells denote reproducibility errors.}
\label{fig:synthetic-data}
\end{figure}

@@

We
processed a set S of 94 subjects randomly selected in the S500 HCP 
release\footnote{\url{https://db.humanconnectome.org}} of the Human 
Connectome Project~\cite{glasser2013minimal}, in three execution 
conditions with different versions of the CentOS operating system 
(5.11, 6.8 and 7.2 -- referred as C5, C6 and C7), using the 
PreFreesurfer and Freesurfer pipelines described 
in~\cite{glasser2013minimal} and available on 
GitHub\footnote{\url{https://github.com/Washington-University/Pipelines/releases/tag/v3.19.0}}. 
For each pipeline, we identified the set F of files produced for all 
subjects in all conditions. For each condition pair and each pipeline, 
we computed a binary reproducibility matrix U of size $|F|\times|S|$, 
where $U_{i,j}$ is true if and only if file $i$ of subject $j$ was 
different in each condition. Rows of $U$ were ordered by ascending file 
modification time in a random subject in S.

@@

\begin{figure}[h!]
  \centering
  \begin{subfigure}[b]{0.45\columnwidth}
        \includegraphics[width=\columnwidth]{data/Utility_Matrix/PreFreeSurfer/PFS_5v6_utility_matrix.png}
  \caption{PFS, C5 vs C6}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\columnwidth}
         \includegraphics[width=\columnwidth]{data/Utility_Matrix/PreFreeSurfer/PFS_5v7_utility_matrix.png}
  \caption{PFS, C5 vs C7}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\columnwidth}
        \includegraphics[width=\columnwidth]{data/Utility_Matrix/PreFreeSurfer/PFS_6v7_utility_matrix.png}
  \caption{PFS, C6 vs C7}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\columnwidth}
        \includegraphics[width=\columnwidth]{data/Utility_Matrix/FS-100files/FS-First-bound-100files.png}
  \caption{FS (100 files), C6 vs C7}
  \end{subfigure}
  \caption{Utility matrices for PreFreesurfer (PFS) and Freesurfer (FS). White cells denote reproducibility errors.}
    \label{fig:utility-matrices}
\end{figure}

@@

\begin{figure*}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-2-types.pdf}
        \caption{2 subject types}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-4-types.pdf}
        \caption{4 subject types}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-8-types.pdf}
        \caption{8 subject types}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-16-types.pdf}
        \caption{16 subject types}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-32-types.pdf}
        \caption{32 subject types}
\end{subfigure}
\hfill
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-64-types.pdf}
        \caption{64 subject types}
\end{subfigure}
\caption{Accuracy results on synthetic data, ALS \emph{without} bias.}
\label{fig:results-synthetic}
\end{figure*}

@@

\begin{figure*}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-2-types.pdf}
        \caption{2 subject types}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-4-types.pdf}
        \caption{4 subject types}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-8-types.pdf}
        \caption{8 subject types}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-16-types.pdf}
        \caption{16 subject types}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-32-types.pdf}
        \caption{32 subject types}
\end{subfigure}
\hfill
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-64-types.pdf}
        \caption{64 subject types}
\end{subfigure}
\caption{Accuracy results on synthetic data, ALS \emph{with} bias.}
\label{fig:results-synthetic-als-bias}
\end{figure*}

@@

\begin{figure*}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-5v6.pdf}
        \caption{PFS, CentOS5 vs CentOS6}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-5v7.pdf}
        \caption{PFS, CentOS5 vs CentOS7}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-6v7.pdf}
        \caption{PFS, CentOS6 vs CentOS7}
\end{subfigure}\hfill
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/FS-100files/ALS-FS100files.pdf}
        \caption{FS, CentOS6 vs CentOS7}
\end{subfigure}
\caption{Accuracy results on PreFresurfer (PFS) and Freesurfer (FS) data, ALS \emph{without} bias.}
\label{fig:results-real-als}
\end{figure*}

@@

Figure~\ref{fig:results-real-als-bias} shows the accuracy for ALS with 
bias. From a training ratio of 0.5, all methods perform well for all 
datasets, except complete columns in 
Figure~\ref{fig:pfs-c5vsc7-bias}. All methods except RFNU, RFNTL and 
RFNTS also perform well for a training ratio lower than 0.5. Overall, 
the accuracy is much higher than without bias, due to the fact that the 
file biases are very strong. In the remainder, all the 
results are obtained using ALS without bias.

\begin{figure*}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-5v6.pdf}
        \caption{PFS, CentOS5 vs CentOS6}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-5v7.pdf}
        \caption{PFS, CentOS5 vs CentOS7}
        \label{fig:pfs-c5vsc7-bias}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-6v7.pdf}
        \caption{PFS, CentOS6 vs CentOS7}
\end{subfigure}\hfill
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/FS-100files/ALS-Bias-FS100files.pdf}
        \caption{FS, CentOS6 vs CentOS7}
\end{subfigure}
\caption{Accuracy results on PreFresurfer (PFS) and Freesurfer (FS) data, ALS \emph{with} bias.}
\label{fig:results-real-als-bias}
\end{figure*}

@@

Figure~\ref{fig:roc} compares the sampling methods in the ROC space, 
for a training ratio of 0.9, on the synthetic and Freesurfer dataset. 
The PreFreesurfer dataset is not included since specificity of RFNTL, 
RFNU, RS and complete rows is undefined at this training ratio (the 
test set only contains positive elements). The average sensitivity and specificity values 
are reported in Table~\ref{table:roc}, which confirms that RFNU is the best 
performing method on average.

\begin{figure*}
\includegraphics[width=\columnwidth]{data/results/roc/roc.pdf}
\includegraphics[width=\columnwidth]{data/results/roc/roc-closeup.pdf}
\caption{Comparison of the sampling methods in the ROC space for the 6 synthetic datasets and Freesurfer (ALS without bias). Right: entire dataset. Left: close-up on the top-left part.}
\label{fig:roc}
\end{figure*}

\begin{table}
\centering
\begin{tabular}{ccc}
& Sensitivity & Specificity \\
\hline
Complete Columns & 0.53 & 0.97\\
Complete Rows & 0.43 & 0.89\\
Random Subjects & 0.88 & 0.99\\
RFNU & 0.92 & 0.99 \\
RFNTL & 0.81 & 0.97\\
RFNTS & 0.65 & 0.93 \\
Random Unreal & 1 & 1
\end{tabular}
\caption{Average sensitivity and specificity for the synthetic datasets and Freesurfer ($\alpha=0.9$, ALS without bias).}
\label{table:roc}
\end{table}

\subsection{Effect of the number of factors} Figure~\ref{fig:factors} 
shows the effect of the number of factors used in the ALS optimization 
for the RFNU method and the synthetic dataset with 8 subject types (3 
blocks of files). For training ratios greater than 0.5, the accuracy 
with 3 factors is substantially higher than with 2 factors. Beyond 3, 
the number of factors does not have any effect, which shows that the 
data is best 
explained by 3 factors. Figure~\ref{fig:factors3d} confirms that 3 
factors are enough to separate the files of this dataset in 3 
blocks, and the subjects in 8 types.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.6\columnwidth]{figures/RFNU_FS100F_ALS_06_test_data_matrix_run1.png}
\caption{Prediction results for RFNU on the Freesurfer dataset, $\alpha=0.6$.}
\label{fig:error-locality}
\end{figure}

@@

\newpage

\onecolumn

\begin{figure}
\begin{minipage}{0.45\textwidth}
\includegraphics[width=\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Factors/ALS-8-types-ranks.pdf}
\caption{Effect of the number of factors used in ALS, (RFNU, synthetic dataset, 8 types, 5 iterations).}
\label{fig:factors}
\end{minipage}\hfill
\begin{minipage}{0.45\textwidth}
\includegraphics[width=\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Iterations-rank50/ALS-8-types-iteration.pdf}
\caption{Effect of the number of iterations used in ALS, (RFNU, synthetic dataset, 8 types, 50 factors).}
\label{fig:iterations}
\end{minipage}
\end{figure}

\begin{figure*}
\begin{subfigure}{0.5\columnwidth}
\includegraphics[width=\columnwidth]{./data/results/latent-factors/5i-3f-ALS-r1-08-userFactors.pdf}
\caption{Subject factors}
\end{subfigure}
\hfill
\begin{subfigure}{0.5\columnwidth}
\includegraphics[width=\columnwidth]{./data/results/latent-factors/5i-3f-ALS-r1-08-itemFactors.pdf}
\caption{File factors}
\end{subfigure}
\caption{Subject and file factors produced by collaborative filtering (RFNU, synthetic dataset, 8 types, 3 factors, 5 iterations).}
\label{fig:factors3d}
\end{figure*}

\begin{figure*}
\begin{subfigure}[b]{0.3\columnwidth}
        \includegraphics[width=\columnwidth]{figures/RFNU_Syn_8_ALS_09_test_data_matrix_run1.png}
        \caption{RFNU: $U(0.8N_f, N_f)$}
        \label{fig:overlap-rfnu}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.3\columnwidth}
        \includegraphics[width=\columnwidth]{figures/RFNT-L_Syn_8_ALS_09_test_data_matrix_run2.png}
        \caption{RFNTL: $T(0.85N_f, 0.85N_f, N_f)$}
        \label{fig:overlap-rfntl}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.3\columnwidth}
        \includegraphics[width=\columnwidth]{figures/RFNT-S_Syn_8_ALS_09_test_data_matrix_run1.png}
        \caption{RFNTS: 0.3$T(0, N_f, N_f)$+0.7$N_f$}
        \label{fig:overlap-rfnts}
\end{subfigure}
\caption{Comparison between RFNU, RFNTL and RFNTS on synthetic dataset with 8 types, $\alpha=0.9$.}
\label{fig:overlap}
\end{figure*}

>>>>

% new commands
\newcommand{\todo}[1]{\marginpar{\parbox{18mm}{\flushleft\tiny\color{red}\textbf{TODO}:
      #1}}}
\newcommand{\note}[1]{
  \color{blue}\emph{[Note: #1]}
  \color{black}
}
\newcommand{\english}[1]{\uwave{#1}}

@@

\begin{figure}
\centering
        %\begin{subfigure}[b]{\columnwidth}
                  %\includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/1_SubjectType_utility_matrix.png}
                  %\caption{1 type}
        %\end{subfigure}
        \begin{subfigure}[b]{0.3\columnwidth}
                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/2_SubjectType_utility_matrix.png}
                  \caption{2 types}
        \end{subfigure}
                \begin{subfigure}[b]{0.3\columnwidth}
                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/8_SubjectType_utility_matrix.png}
                  \caption{8 types}
        \end{subfigure}
                \begin{subfigure}[b]{0.3\columnwidth}
                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/64_SubjectType_utility_matrix.png}
                  \caption{64 types}
        \end{subfigure}
\caption{Synthetic reproducibility matrices. White cells denote reproducibility errors.}
\label{fig:synthetic-data}
\end{figure}

@@

We
processed a set S of 94 subjects randomly selected in the S500 HCP 
release\footnote{\url{https://db.humanconnectome.org}} of the Human 
Connectome Project~\cite{glasser2013minimal}, in two execution 
conditions with different versions of the CentOS operating system 
(6.8 and 7.2 -- referred as C6 and C7), using the 
PreFreesurfer and Freesurfer pipelines described 
in~\cite{glasser2013minimal} and available on 
GitHub\footnote{\url{https://github.com/Washington-University/Pipelines/releases/tag/v3.19.0}}. 
For each pipeline, we identified the set F of files produced for all 
subjects in all conditions. For each condition pair and each pipeline, 
we computed a binary reproducibility matrix U of size $|F|\times|S|$, 
where $U_{i,j}$ is true if and only if file $i$ of subject $j$ was 
different in each condition. Rows of $U$ were ordered by ascending file 
modification time in a random subject in S.

@@

\begin{figure}[h!]
  \centering
  \begin{subfigure}[b]{0.45\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/Utility_Matrix/PreFreeSurfer/PFS_6v7_utility_matrix.png}
  \caption{PFS}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/Utility_Matrix/FS-100files/FS-First-bound-100files.png}
  \caption{FS (100 files)}
  \end{subfigure}
  \caption{Utility matrices for PreFreesurfer (PFS) and Freesurfer (FS). White cells denote reproducibility errors.}
    \label{fig:utility-matrices}
\end{figure}

@@

\begin{figure*}
\begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-2-types.pdf}
        \caption{2 subject types}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-8-types.pdf}
        \caption{8 subject types}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-64-types.pdf}
        \caption{64 subject types}
\end{subfigure}
\caption{Accuracy results on synthetic data, ALS \emph{without} bias.}
\label{fig:results-synthetic}
\end{figure*}
\begin{figure*}
\centering
\begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-2-types.pdf}
        \caption{2 subject types}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-8-types.pdf}
        \caption{8 subject types}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-64-types.pdf}
        \caption{64 subject types}
\end{subfigure}
\caption{Accuracy results on synthetic data, ALS \emph{with} bias.}
\label{fig:results-synthetic-als-bias}
\end{figure*}

@@

@@

\begin{figure}
\begin{subfigure}[b]{0.5\columnwidth}
        \includegraphics[width=\textwidth]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-6v7.pdf}
        \caption{PFS}
\end{subfigure}\hfill
\begin{subfigure}[b]{0.5\columnwidth}
        \includegraphics[width=\textwidth]{data/results/means_of_results/ALS/FS-100files/ALS-FS100files.pdf}
        \caption{FS}
\end{subfigure}
\caption{Accuracy results on PreFresurfer (PFS) and Freesurfer (FS) data, ALS \emph{without} bias.}
\label{fig:results-real-als}
\end{figure}

@@

Figure~\ref{fig:results-real-als-bias} shows the accuracy for ALS with 
bias. From a training ratio of 0.5, all methods perform well for all 
datasets. All methods except RFNU, RFNTL and 
RFNTS also perform well for a training ratio lower than 0.5. Overall, 
the accuracy is much higher than without bias, due to the fact that the 
file biases are very strong. In the remainder, all the 
results are obtained using ALS without bias.

\begin{figure}
\centering
\begin{subfigure}[b]{0.5\columnwidth}
        \includegraphics[width=\textwidth]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-6v7.pdf}
        \caption{PFS}
\end{subfigure}\hfill
\begin{subfigure}[b]{0.5\columnwidth}
        \includegraphics[width=\textwidth]{data/results/means_of_results/ALS-Bias/FS-100files/ALS-Bias-FS100files.pdf}
        \caption{FS}
\end{subfigure}
\caption{Accuracy results on PreFresurfer (PFS) and Freesurfer (FS) data, ALS \emph{with} bias.}
\label{fig:results-real-als-bias}
\end{figure}

@@

Figure~\ref{fig:roc} compares the sampling methods in the ROC space, 
for a training ratio of 0.9, on the synthetic and Freesurfer dataset. 
The PreFreesurfer dataset is not included since specificity of RFNTL, 
RFNU, RS and complete rows is undefined at this training ratio (the 
test set only contains positive elements). The average sensitivity and specificity values 
are reported in Table~\ref{table:roc}, which confirms that RFNU is the best 
performing method on average.
\begin{figure}
\centering
\includegraphics[width=0.5\columnwidth]{data/results/roc/roc.pdf}\hfill
\includegraphics[width=0.5\columnwidth]{data/results/roc/roc-closeup.pdf}
\caption{Comparison of the sampling methods in the ROC space for the 3 synthetic datasets and Freesurfer (ALS without bias). Right: entire dataset. Left: close-up on the top-left part.}
\label{fig:roc}
\end{figure}
\begin{table}
\centering
\begin{tabular}{ccc}
& Sensitivity & Specificity \\
\hline
Complete Columns & 0.63 & 0.99\\
Complete Rows & 0.50 & 0.91\\
Random Subjects & 0.89 & 0.98\\
RFNU & 0.90 & 0.98 \\
RFNTL & 0.82 & 0.97\\
RFNTS & 0.72 & 0.94 \\
Random Unreal & 1.00 & 0.99
\end{tabular}
\caption{Average sensitivity and specificity for the synthetic datasets and Freesurfer ($\alpha=0.9$, ALS without bias).}
\label{table:roc}
\end{table}

\begin{figure}
\centering
\includegraphics[width=0.6\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Factors/ALS-8-types-ranks.pdf}
\caption{Effect of the number of factors used in ALS, (RFNU, synthetic dataset, 8 types, 5 iterations).}
\label{fig:factors}
\end{figure}
\begin{figure}
\begin{subfigure}{0.5\columnwidth}
\includegraphics[width=\columnwidth]{./data/results/latent-factors/5i-3f-ALS-r1-08-userFactors.pdf}
\caption{Subject factors}
\end{subfigure}\hfill
\begin{subfigure}{0.5\columnwidth}
\includegraphics[width=\columnwidth]{./data/results/latent-factors/5i-3f-ALS-r1-08-itemFactors.pdf}
\caption{File factors}
\end{subfigure}
\caption{Subject and file factors produced by collaborative filtering (RFNU, synthetic dataset, 8 types, 3 factors, 5 iterations).}
\label{fig:factors3d}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.6\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Iterations-rank50/ALS-8-types-iteration.pdf}
\caption{Effect of the number of iterations used in ALS, (RFNU, synthetic dataset, 8 types, 50 factors).}
\label{fig:iterations}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}[b]{0.4\columnwidth}
        \includegraphics[width=\columnwidth]{figures/RFNU_Syn_8_ALS_09_test_data_matrix_run1.png}
        \caption{RFNU: $U(0.8N_f, N_f)$}
        \label{fig:overlap-rfnu}
\end{subfigure}\\
\begin{subfigure}[b]{0.4\columnwidth}
        \includegraphics[width=\columnwidth]{figures/RFNT-L_Syn_8_ALS_09_test_data_matrix_run2.png}
        \caption{RFNTL: $T(0.85N_f, 0.85N_f, N_f)$}
        \label{fig:overlap-rfntl}
\end{subfigure}\\
\begin{subfigure}[b]{0.4\columnwidth}
        \includegraphics[width=\columnwidth]{figures/RFNT-S_Syn_8_ALS_09_test_data_matrix_run1.png}
        \caption{RFNTS: 0.3$T(0, N_f, N_f)$+0.7$N_f$}
        \label{fig:overlap-rfnts}
\end{subfigure}
\caption{Comparison between RFNU, RFNTL and RFNTS on synthetic dataset with 8 types, $\alpha=0.9$.}
\label{fig:overlap}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.6\columnwidth]{figures/RFNU_FS100F_ALS_06_test_data_matrix_run1.png}
\caption{Prediction results for RFNU on the Freesurfer dataset, $\alpha=0.6$.}
\label{fig:error-locality}
\end{figure}

\subsection{Effect of the number of factors} Figure~\ref{fig:factors} 
shows the effect of the number of factors used in the ALS optimization 
for the RFNU method and the synthetic dataset with 8 subject types (3 
blocks of files). For training ratios greater than 0.5, the accuracy 
with 3 factors is substantially higher than with 2 factors. Beyond 3, 
the number of factors does not have any effect, which shows that the 
data is best 
explained by 3 factors. Figure~\ref{fig:factors3d} confirms that 3 
factors are enough to separate the files of this dataset in 3 
blocks, and the subjects in 8 types. \enlargethispage{5mm}

@@

@@
